\vspace{-.2in} Squint: Lossy Hierarchical Compression on Symbol Streams \vspace{-.1in}

### 2012-12-12 tex/paper.tex
Future Work section

\begin{algorithm}[h]
\caption{Cluster Lossifier Algorithm}
\label{cluster_alg}
\begin{algorithmic}[1]
\Procedure{Cluster-Sim}{$g$} \Comment{Simplify grammar g}
  \While{there are similar variables to replace}
    \State $clusters \gets ()$
    \For{$var_1 \rightarrow rhs_1 \in g$}
      \For{$c \in clusters$}
        \State $(var_2 \rightarrow rhs_2) \gets $ first variable in $c$
        \State $str_{i} \gets expand(rhs_i)$
        \If{$lsim(str_{1},str_{2})<\epsilon$}
          \State add $var_1$ to $c$
          \State break
        \EndIf
      \EndFor
      \If{$var_1$ hasn't been added to a cluster}
        \State Add $var_1$ to a new cluster in $clusters$
      \EndIf
    \EndFor
    \State save a mapping $m$ from variables to sizes
    \For{Cluster $c \in clusters$}
      \State replace all $var \in c$ with the smallest (smallest w.r.t. $m$).
    \EndFor
  \EndWhile
\EndProcedure
\end{algorithmic}
\end{algorithm}

@@

\subsection{Future Work}
* Better ways to set epsilon to maximize value / cost for different size and types
* Better ways to quantify preservation of hierarchies
* How to find near `self-similarities' that aren't captured by a rule
* Iterating lossify and reduce in a cycle

>>>>

\begin{algorithm}[h]
\caption{Cluster Lossifier Algorithm}
\label{cluster_alg}
\begin{algorithmic}[1]
\Procedure{Cluster-Sim}{$g$} \Comment{Simplify grammar g}
  \While{there are similar variables to replace}
    \State $clusters \gets ()$
    \For{$var_1 \rightarrow rhs_1 \in g$}
      \For{$c \in clusters$}
        \State $(var_2 \rightarrow rhs_2) \gets $ first variable in $c$
        \State $str_{i} \gets expand(rhs_i)$
        \If{$lsim(str_{1},str_{2})<\epsilon$}
          \State add $var_1$ to $c$
          \State break
        \EndIf
      \EndFor
      \If{$var_1$ hasn't been added to a cluster}
        \State add $var_1$ to a new cluster in $clusters$
      \EndIf
    \EndFor
    \State save a mapping $m$ from variables to sizes
    \For{Cluster $c \in clusters$}
      \State replace all $var \in c$ with the smallest (smallest w.r.t. $m$).
    \EndFor
  \EndWhile
\EndProcedure
\end{algorithmic}
\end{algorithm}

@@

\subsection{Future Work}

There are many further directions to explore in the area of lossy grammar
compression.  One immediate direction for future work is to develop additional
lossifier algorithms, or to determine techniques for improving our existing
ones.  One shortcoming of our \Cluster algorithm is that, by replacing clusters
with the shortest rule, we lose both fidelity in the final expanded stream
\emph{and} structure in the simplified grammar.  Replacing each cluster with
the most frequently-appearing rule could improve this situation, at some small
cost to the final compression ratio (small because all rules in a cluster are
similar in size).  Unfortunately, we were unable to devise an efficient
algorithm to perform this sort of replacement without accidentally introducing
cycles.

Investigating the intuition---or perhaps, providing some methodology---for
choosing the parameter $\epsilon$ would also be useful.  Ideally, we could
reliably choose $\epsilon$ in such a way that we maximize the ratio of
compression to fidelity loss.  Investigating the effect that $\epsilon$ has for
additional types of structured data might shed some light on this problem.

Additional metrics for lossified grammars are also an important direction to
consider.  Ultimately, our goal is to compress the \emph{hierarchical
structure} of data, rather than the data itself, efficiently and with high
fidelity.  However, we were only able to directly measure how well we preserved
structure on contrived data, such as rep-n.  On real datasets, we instead made
a first-order approximation by comparing the fully-expanded output streams.
Some broadly-applicable metrics for comparing hierarchical structures would
significantly improve the evaluability of lossy grammar compression techniques.
